Supplementary Materials

### 2018-03-25 paper/perturbation.tex
add json print out
update structure
update paper structure
update layout of the paper
add figure for end2end
update tasks
minor fix

\section{Error Analysis Via Input Perturbation}

Understand where and how does a model fail is the first step to improve the
model performance.
Prediction accuray, i.e., the percentage of the correct prediction according to
the ground truth label, is the standard technique to verify the performance
of a model on a given supervised task.
%
The accuracy alone does not tell us the whole story, it provides no
information on the specific example and the condition that lead to a failure.
%
Often, the user need to examine individual failure examples to dignostic the
issue and identify the weakness of the model.
%
However, the model may be unstable and generate the right prediction for the wrong
reason (e.g., by picking up noise in the data that is not the intended features),
therefore, we are likely to miss some important failure condition by just looking
at the failure cases.
%
An in depth analysis of the error made by the model requires the verification of
the robustness of the prediction.
%
One powerful tool to assess robustness is through the application of small
perturbation in the input and then check the variation of the prediction.
%
For example, we can replace noun and verb in the sentences with words of
similar/same meaning, such an operation is often carried out by domain experts
(subconsciously) when they try to figure out the potential issue of a model.
%
In another work, the perturbation of the input allow us to do a sensitivity
analysis on the prediction.
%
In this work, we introduce an synonyms perturbation scheme that automatically
generate the perturbation and generate the prediction and summarized the prediction
variation.
%

\begin{itemize}
    \item perturbation prediction change ratio
    \item prediction distance (KL divergines) to original prediction
    \item attention change distance
\end{itemize}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{
 Perturbation-Driven Exploration of the Language Inference Model.
 }
\label{fig:modelPipeline}
\end{figure}

\subsection{Perturbation-Driven Exploration}

Fig.~\ref{fig:modelPipeline}

Understand where and how does a model fail is the first step to improve the
model performance.
Prediction accuracy, i.e., the percentage of the correct prediction according to
the ground truth label, is the standard technique to verify the performance
of a model on a given supervised task.
%
The accuracy alone does not tell us the whole story, it provides no
information on the specific example and the condition that lead to a failure.
%
Often, the user need to examine individual failure examples to diagnostic the
issue and identify the weakness of the model.
%
However, the model may be unstable and generate the right prediction for the wrong
reason (e.g., by picking up noise in the data that is not the intended features),
therefore, we are likely to miss some important failure condition by just looking
at the failure cases.
%
An in depth analysis of the error made by the model requires the verification of
the robustness of the prediction.
%
One powerful tool to assess robustness is through the application of small
perturbation in the input and then check the variation of the prediction.
%
For example, we can replace noun and verb in the sentences with words of
similar/same meaning, such an operation is often carried out by domain experts
(subconsciously) when they try to figure out the potential issue of a model.
%
In another work, the perturbation of the input allow us to do a sensitivity
analysis on the prediction.
%
In this work, we introduce an synonyms perturbation scheme that automatically
generate the perturbation and generate the prediction and summarized the prediction
variation.
%

% \begin{itemize}
%     \item perturbation prediction change ratio
%     \item distribution distance (KL divergence) to original prediction
%     \item attention change distance
% \end{itemize}

### 2018-03-25 paper/pipeline.tex
minor fix

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:modelPipeline}
\end{figure}

\section{NLIVis Design}
In this section, we describe the design of the NLIVis system, which address the tasks described in the previous section.

\shusen{overview of the system}

>>>>

\section{NLIVis Design}
We describe the design of the NLIVis system, which address the visualization tasks described in the previous section. 
%
First, we discuss the perturbation-driven paradigm that is central to the achieving the visualization tasks.
%
Then, we describe in detail the five major components of the proposed system, namely, all pair summary view, sentence view, attention view, prediction view, pipeline view.

### 2018-03-25 paper/relatedWorks.tex
minor fix

\noindent\textbf{Visual Exploration of Neural Network Models.}
Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works has dedicated to the neural network models.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possibility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training process, so they can provide design guideline to the deep neutral network architect.

>>>>

\noindent\textbf{Visual Exploration of Neural Network Models.}
Due to the effectiveness for exploring complex relationships, visualization have long been adopted for interpreting neural network models~\cite{TzengMa2005}.
Recently, the increasingly apparent interpretability challenge for deep neural network model motivate the introduction of many visualization works that dedicated to the neural network models.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possibility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training process, so they can provide design guideline to the deep neutral network architect.

### 2018-03-25 paper/sentence.tex
minor fix

\subsection{All Pair Summary View}
\begin{itemize}
\item How go from 10k pair to one pair
\item How constitute interesting example
\item How to get a sense of overall prediction result
\end{itemize}

\subsection{Sentence View}
\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}

>>>>

\subsection{All Pairs Summary View}
\label{sec:allPairs}
Since we can only focus on one individual example at a time for detail analysis, 
how to pick an single pair of sentence from the development or test dataset (for the SNLI dataset, each of the these set consists of close to $10k$ examples) is an obvious challenge.
%
In addition, we also want to obtain certain high-level understand of how the whole set behave, beyond the information the prediction accuracy provide.

%The all pair
\begin{itemize}
\item How to go from 10k pair to one pair
\item What constitute interesting example
\item How to get a sense of overall prediction result
\end{itemize}

\subsection{Sentence View}
The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
%
Add user customized sentences.

\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}
